Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-29 draft/paper1_rachel.tex
Edit sample selection 2

    $M_{\mathrm{halo}}$ denotes halo mass in general whereas $M_{\rm 200b}$ is 
    explicitly defined as $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
    is the radius at which the mean interior density is equal to 200 times
    the mean matter density ($\bar{\rho}$).

@@

    Here we limit our study to the very high-mass end where the majority of galaxies 
    have either a spectroscopic redshift or a robust red-sequence photo-$z$ from the 
    \redm{} galaxy cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}).  
\rachel{You require it to be a redmapper cluster member?  Or do you mean it must be part of the redmagic galaxy sample?  I do not fully understand the logic in using redmapper rather than redmagic.}
We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team\footnote{It is created by matching HSC objects with all publicly available 
    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). 
    The spec-$z$ quality flag from different catalogs are homogenized into a single 
    flag that indicates secure redshifts. \rachel{Is there a paper or a note at the data release page that we could reference so readers can check out how this was defined?}}.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

    Objects without a spectroscopic redshift are matched with central 
    galaxies from the \redm{} SDSS DR8 (\citealt{SDSSDR8}) catalog using a $2.0^{\arcsec}$ matching radius. Matched objects with a red-sequence photo-$z$ ($0.3 \leq z_{\lambda} < 0.5$) are included in our sample. The accuracy of the red-sequence photo-$z$ is sufficient (median 
    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with spec-$z$) 
    for the goal of this work.
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    In total, at $0.3 \leq z \leq 0.5$, our sample consists of 25286 galaxies with 
    reliable redshift information (referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    The majority of our redshifts come from the BOSS and SDSS ``legacy'' LRG samples. The GAMA survey provides an additional $14$\% of spec-$z$.
\rachel{This is only of order 1\% of the original sample.  Do we understand why?  Of particular concern are cuts that affect survey homogeneity; e.g., in the area covered by GAMA vs.\ the area not covered by GAMA, might the sample look different?  What will that do to this study?}
We choose the redshift range of $0.3 \leq z \leq 0.5$ to make sure that 
    (1) The inner region of massive galaxies can be resolved, and \mstar{} within 
    10 kpc can be reliably measured; 
    (2) The background noise and cosmological dimming are not major issues and the 
    \mden{} profile can be measured out to $>100$ kpc; 
    (3) Redshift evolution in the stellar population properties can be largely 
    ignored.  
    Also at higher redshift, the completeness of the spec-$z$ sample starts to decline. And finally, the over-subtraction of the background level becomes a more serious issue at lower redshifts.  We will now describe our one-dimensional photometric analysis  (\S \ref{sec:ellipse}) and our stellar mass estimates (\S \ref{sec:mstar}). We will then define the final sample in \S \ref{sec:final}.

@@

    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
    galaxies and to measure their one-dimensional stellar mass surface 
    density profiles (\mden{}). 
    This 1-D method is less affected by the issues mentioned above. 
    Also, we will only study galaxies in the radial range where we are not 
    sensitive to either the PSF ($r<3-5$ kpc) or the background subtraction 
    ($r>100$ kpc). \rachel{Here too I think we have to be careful about how we say this.  The PSF is not irrelevant outside of the inner part of the profile.  It's just less important.  Perhaps say `\dots where we are less sensitive to the PSF or the background subtraction\dots'}

>>>>

    Halo mass is defined as $M_{\rm 200b}$ as 
    $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
    is the radius at which the mean interior density is equal to 200 times
    the mean matter density ($\bar{\rho}$).

@@

    Here we limit our study to the very high-mass end where the majority of galaxies 
    have either a spectroscopic redshift or a robust red-sequence photo-$z$ from the 
    \redm{} galaxy cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}).

    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team.
    It is created by matching HSC objects with a series of publicly available 
    spectroscopic redshifts (e.g.\ SDSS DR12 \citealt{SDSSDR12}; 
    GAMA DR2 \citealt{Liske2015}). 
    The spec-$z$ quality flag from different catalogs are homogenized into a single 
    flag that indicates secure redshifts.
    Please see Section 4.4.2 of \citet{HSC_DR1} for details of this catalog.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

    Objects without a spectroscopic redshift are matched with central 
    galaxies from the \redm{} SDSS DR8 (\citealt{Rykoff2014}) catalog using a 
    $2.0^{\arcsec}$ matching radius. 
    Matched objects with a red-sequence photo-$z$ ($0.3 \leq z_{\lambda} < 0.5$) are 
    included in our sample. 
    The accuracy of the red-sequence photo-$z$ is sufficient (median 
    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with spec-$z$) 
    for the goal of this work.
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    In total, at $0.3 \leq z \leq 0.5$, our sample consists of 25286 galaxies with 
    reliable redshift information (referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    The majority of our redshifts comes from the BOSS and SDSS ``legacy'' LRG samples. 
    The GAMA survey provides an additional $14$\% of spec-$z$.
    Although the GAMA survey only covers parts of the \texttt{S15B} data release, hence affects 
    the homogeneity of our sample, it will not affect the results of this work.
    We will discuss this more in \S \ref{sec:final}.

    We choose the redshift range of $0.3 \leq z \leq 0.5$ to make sure that 
    (1) The inner region of massive galaxies can be resolved, and \mstar{} within 
    10 kpc can be reliably measured; 
    (2) The background noise and cosmological dimming are not major issues and the 
    \mden{} profile can be measured out to $>100$ kpc; 
    (3) Redshift evolution in the stellar population properties can be largely 
    ignored.  
    Also at higher redshift, the completeness of the spec-$z$ sample starts to decline. 
    And finally, the over-subtraction of the background level becomes a more serious 
    issue at lower redshifts.  
    We will now describe our one-dimensional photometric analysis (\S \ref{sec:ellipse}) 
    and our stellar mass estimates (\S \ref{sec:mstar}). 
    We will then define the final sample in \S \ref{sec:final}.

@@

    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
    galaxies and to measure their one-dimensional stellar mass surface 
    density profiles (\mden{}). 
    This 1-D method is less affected by the issues mentioned above. 
    Also, we will only study galaxies in the radial range where we are less 
    sensitive to either the PSF ($r<5-6$ kpc) or the background subtraction 
    ($r>100$ kpc).
    The region 
    It is worth noting that the PSF
